Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives

### 2017-06-21 presentation/presentation.tex
[major] add improved ppt

	\vskip 1em
	\begin{block}{Major challenges involved}
		\begin{itemize}
			\item Close interaction of the robot with non-rigid clothing article
			\item Safe human-robot interaction
			\item Accurate estimation of human-cloth relationship
		\end{itemize}
	\end{block}
\end{frame}

@@

	\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.5\textwidth}
			Towner \textit{et al.}\footnotemark, ~Identifying and manipulating clothing article by dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
					\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
					\item[\color{red}{$\times$}] Highly depends on simulated contour information.
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{towner_2011}
			}
		\end{column}

		\begin{column}{0.5\textwidth}
			Tamei \textit{et al.}\footnotemark, ~Clothing assistance with dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item[\color{green}{\checkmark}] Used Reinforcement
					      learning (RL)
					\item[\color{green}{\checkmark}] Topology coordinates for human and cloth extremities relationship
					\item[\color{red}{$\times$}] Limited generalization capability for new postures
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{tamei_2011}
			}
		\end{column}
	\end{columns}

@@

	%	\vskip 1em
	%	Now add a forcing term $f$ on eq(\ref{eq:attractor}) that will let us to modify this trajectory
	The system is defined as
	\vskip -1em
	\begin{equation}
		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
		\label{eq:attractor_with_f}
	\end{equation}
	%\vskip -0.5em
	{\small
		where:
		\vskip -0.6em
		\begin{itemize}
			\itemsep-0.2em
			\item $y$ is system state and $g$ is goal state
			\item $\alpha$ and $\beta$ are gain terms
			\item $f$ is nonlinear function defined over time
		\end{itemize}
	}

@@

\begin{frame}{Forcing function $f$}
	$f$ is defined as
	\begin{equation}
		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
		\label{eq:cs_with_f}
	\end{equation}

	where:
	\begin{itemize}
		\item $y_0$ is the initial state of the system
		\item $w_i$ is a weighting for a given basis function $\psi_i$
		\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
	\end{itemize}

	\vskip -1em
	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=2.1cm]{psi_activation}
				\vskip -0.3em
				\caption{$\psi$ Activation}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=2.1cm]{weighted_summation}
				\vskip -0.3em
				\caption{Weighted Summation}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Imitating a desired path}
	\linespread{1.4}
	The desired forcing term $f$ which affects the system acceleration, is written as
	\vskip -1.5em
	\begin{equation}
		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
		\label{eq:imitate_f}
	\end{equation}
	\vskip -0.5em
	{\small
		where 
		\vskip -1em
		\begin{itemize}
			\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
		\end{itemize}
	}
	\vskip-0.5em
	\begin{exampleblock}{}
		Choose the weights over the basis functions i.e., minimize\footnotemark
		\vskip-2em
		\begin{equation}
			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
			\label{eq:minize_fd}
		\end{equation}
	\end{exampleblock}
	\vskip-0.5em
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{imitate_path}
	\end{figure}
	\vskip-1.5em
	\footcitetext{schaal2002scalable}
\end{frame}

@@

\section{Results}
\begin{frame}{Results}
	\begin{columns}[b]
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{various_posture}
				\caption{Old \& modified posture of mannequin}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{trajectory}
				\caption{Left arm trajectories of Baxter Robot}
			\end{figure}
		\end{column}
	\end{columns}

	\vskip 1em
	\centering{
		\href{run:./videos/video.mp4}{\beamerbutton{Video demonstration}}
	}
\end{frame}

\section{Conclusion and Discussion}
\begin{frame}{Conclusion and Discussion}
	\linespread{1.5}

	\begin{itemize}
		\item Baxter APIs\footcite{fitzgerald2013developing} are used to get the end-effector forces. Raw forces are found noisy in nature.
		\item Result shows that DMPs are able to generalize the movement trajectory
		\item Proposed failure detection method by using force information can detect failures
		\item DMP should incorporate orientation information as well
	\end{itemize}
\end{frame}

>>>>

	\vskip 1em
	\begin{block}{Major challenges involved}
		\begin{itemize}
			\item Close interaction of the robot with non-rigid clothing article
			\item Safe human-robot interaction
			\item Estimation of human-cloth relationship
		\end{itemize}
	\end{block}
\end{frame}

@@

	%\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.5\textwidth}
			Towner \textit{et al.}\footnotemark, ~Manipulating clothing article by dual-arm robot
			{\scriptsize
				\begin{itemize}
					%\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
					%\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
					%\item[\color{red}{$\times$}] Highly depends on simulated contour information.
					\item Used Hidden Markov Model for tracking
					\item Triangulated mesh model for simulating clothing article
					\item Highly depends on simulated contour information.
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{towner_2011}
			}
		\end{column}

		\begin{column}{0.5\textwidth}
			Tamei \textit{et al.}\footnotemark, ~Clothing assistance with dual-arm robot
			{\scriptsize
				\begin{itemize}
					%\item[\color{green}{\checkmark}] Used Reinforcement learning (RL)
					%\item[\color{green}{\checkmark}] Topology coordinates for human and cloth extremities relationship
					%\item[\color{red}{$\times$}] Limited generalization capability for new postures
					\item Used Reinforcement learning (RL)
					\item Topology coordinates for human and cloth extremities relationship
					\item Via-point trajectory with minimum jerk criterion
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{tamei_2011}
			}
		\end{column}
	\end{columns}

@@

	%	\vskip 1em
	%	Now add a forcing term $f$ on eq(\ref{eq:attractor}) that will let us to modify this trajectory
	The system is defined as
	\vskip -1em
	\begin{equation*}
		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
		\label{eq:attractor_with_f}
	\end{equation*}
	%\vskip -0.5em
	{\small
		where:
		\vskip -0.6em
		\begin{itemize}
			\itemsep-0.2em
			\item $y$ is system state and $g$ is goal state
			\item $\alpha$ and $\beta$ are gain terms
			\item $f$ is nonlinear function defined over time
		\end{itemize}
	}

@@

\begin{frame}{Forcing function $f$}
$f$ is defined as
\vskip-2.8em
	\begin{equation*}
		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
		\label{eq:cs_with_f}
	\end{equation*}
\vskip-0.5em
{\small
where:
\vskip-0.8em
	\begin{itemize}
	\setlength\itemsep{0.2em}
		\item $y_0$ is the initial state of the system
		\item $w_i$ is a weighting for a given basis function $\psi_i$
		\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
	\end{itemize}
}
\vskip-1.2em
\begin{exampleblock}{Imitating a desired path}
	The desired forcing term $f$ which affects the system acceleration, is written as
	\vskip-2.4em
	\begin{equation*}
		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
		\label{eq:imitate_f}
	\end{equation*}
	\vskip -0.5em
	{\small
		where
		\vskip -1em
		\begin{itemize}
			\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
		\end{itemize}
	}
Choose the weights over the basis functions i.e., minimize\footnotemark
		\vskip-1em
		\begin{equation*}
			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
			\label{eq:minize_fd}
		\end{equation*}
\end{exampleblock}
\vskip-1.5em
\footcitetext{schaal2002scalable}
\end{frame}

%\begin{frame}{Forcing function $f$}
%	$f$ is defined as
%	\begin{equation}
%		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
%		\label{eq:cs_with_f}
%	\end{equation}
%
%	where:
%	\begin{itemize}
%		\item $y_0$ is the initial state of the system
%		\item $w_i$ is a weighting for a given basis function $\psi_i$
%		\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
%	\end{itemize}
%
%	\vskip -1em
%	\begin{columns}
%		\begin{column}{0.5\textwidth}
%			\begin{figure}
%				\includegraphics[height=2.1cm]{psi_activation}
%				\vskip -0.3em
%				\caption{$\psi$ Activation}
%			\end{figure}
%		\end{column}
%
%		\begin{column}{0.5\textwidth}
%			\begin{figure}
%				\includegraphics[height=2.1cm]{weighted_summation}
%				\vskip -0.3em
%				\caption{Weighted Summation}
%			\end{figure}
%		\end{column}
%	\end{columns}
%\end{frame}
%
%\begin{frame}{Imitating a desired path}
%	\linespread{1.4}
%	The desired forcing term $f$ which affects the system acceleration, is written as
%	\vskip -1.5em
%	\begin{equation}
%		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
%		\label{eq:imitate_f}
%	\end{equation}
%	\vskip -0.5em
%	{\small
%		where
%		\vskip -1em
%		\begin{itemize}
%			\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = %\frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
%		\end{itemize}
%	}
%	\vskip-0.5em
%	\begin{exampleblock}{}
%		Choose the weights over the basis functions i.e., minimize\footnotemark
%		\vskip-2em
%		\begin{equation}
%			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
%			\label{eq:minize_fd}
%		\end{equation}
%	\end{exampleblock}
%	\vskip-0.5em
%	\begin{figure}
%		\includegraphics[width=0.8\textwidth]{imitate_path}
%	\end{figure}
%	\vskip-1.5em
%	\footcitetext{schaal2002scalable}
%\end{frame}

@@

\section{Experiments and Results}
\begin{frame}{Experiments and Results}
	\begin{columns}[b]
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[trim={4cm 0 5cm 0},clip,width=\textwidth]{various_posture}
				\caption{Old \& modified posture of mannequin}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{all_traj}
				\caption{Left arm trajectories of Baxter Robot}
			\end{figure}
		\end{column}
	\end{columns}

	\vskip 1em
	\centering{
		\href{run:./videos/video.mp4}{\beamerbutton{Video Demonstration}}
	}
\end{frame}

\begin{frame}{Accuracy measurement}
	Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space
	\begin{columns}[t]
		\begin{column}{0.4\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{inclination_plus}
				%\caption{Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{success_rate}
				%\caption{Left arm trajectories of Baxter Robot}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

%\begin{frame}{Failure detection using end-effector forces}
%	\begin{exampleblock}{Procedure}
%		\begin{enumerate}
%			\item Each trajectory is computed by calculating the mean.
%			\item The force value is norm of force applied in all three Cartesian directions.
%		\end{enumerate}
%	\end{exampleblock}
%
%	\vskip -1em
%	\begin{columns}[t]
%		\begin{column}{0.3\textwidth}
%			\begin{figure}
%				\includegraphics[width=0.8\textwidth]{failure_scenario_2}
%				\caption{A failure scenario}
%			\end{figure}
%		\end{column}
%
%		\begin{column}{0.5\textwidth}
%			\begin{figure}
%				\includegraphics[width=0.9\textwidth]{position_force}
%				\caption{Forces acting on left arm of Baxter}
%			\end{figure}
%		\end{column}
%	\end{columns}
%\end{frame}

\section{Discussion and Conclusion}
\begin{frame}{Discussion and Conclusion}
	\linespread{1.5}

	\begin{itemize}
		%\item Baxter APIs\footcite{fitzgerald2013developing} are used to get the end-effector forces. Raw forces are found noisy in nature.
		\item Robotic clothing assistance is challenging since it requires cooperative manipulation
		\item Clothing article inherits non-rigid and highly deformable properties
		\item Result shows that DMPs are able to generalize the movement trajectory
		%\item Proposed failure detection method by using force information can detect failures
		\item DMP should incorporate orientation information as well
	\end{itemize}
\end{frame}
